---
title: "Programming Assignment 3: Quiz"
author: "Juan Mateo Rodríguez Sánchez"
date: "30 de enero de 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Quiz Solution

Load the required script: rankall.R
```{r source}
source("./rankall.R")
```


**1. What result is returned by the following code?**

```{r question1}
best("SC", "heart attack")
```


**2. What result is returned by the following code?**

```{r question2}
best("NY", "pneumonia")
```


**3. What result is returned by the following code?**

```{r question3}
best("AK", "pneumonia")
```


**4. What result is returned by the following code?**

```{r question4}
rankhospital("NC", "heart attack", "worst")
```


**5. What result is returned by the following code?**

```{r question5}
rankhospital("WA", "heart attack", 7)
```


**6. What result is returned by the following code?**

```{r question6}
rankhospital("TX", "pneumonia", 10)
```


**7. What result is returned by the following code?**

```{r question7}
rankhospital("NY", "heart attack", 7)
```


**8. What result is returned by the following code?**

```{r question8}
r <- rankall("heart attack", 4)
as.character(subset(r, state == "HI")$hospital)
```


**9. What result is returned by the following code?**

```{r question9}
r <- rankall("pneumonia", "worst")
as.character(subset(r, state == "NJ")$hospital)
```


**10. What result is returned by the following code?**

```{r question10}
r <- rankall("heart failure", 10)
as.character(subset(r, state == "NV")$hospital)
```